---
title: "linear model from Web"
author: "Michael Abdalla"
date: "Put semester and year"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS



### scatterplot
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point()
```

the plot shows there is a positive linear correlation as we have here the sims shown on the y-axis and arm shown on the x-axis 


### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
the number that the is shown is 0.68 which is a positive number and that indicates that the line will travel upward toward the right.

### Inferential  (Build model.1)

  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
The evaluation for the line that fits this is SIMS is equal to `r round(summary(model.1)$coefficients[1],3)` +`r round(summary(model.1)$coefficients[2],3)` * ARM 
the formula needed is y = mx + b to create the line.

#### Predict at target point

```{r}
newdata = data.frame(GRIP = 94, ARM = 88)
predict(model.1, newdata, interval = "prediction", level = .99)
```
this is a prediction interval. how far does one point vary from the other if you take .7 away from 3.13, you'd end up approximately 2.3.

#### scatterplot with model fit
  

## Model 2 SIM~GRIP



### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

 this scatter plot shows that SIMS is correlated with GRIP  where GRIP increases SIMS also increases .

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

### Inferential  (Build model.2)

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```  

#### predict model.2 at target point

```{r}
newdata = data.frame(GRIP = 94, ARM = 88)
predict(model.2, newdata, interval = "prediction", level = .99)
```

the model predicted a SIMS score of -0.536, where the 95% confidence interval -3.932 to 2.860

#### now add the model fit to our plot for model.2

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 


It looks like that the value of Y intercept would be around 1


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```
  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~GRIP+ARM,data=data)
summary.lm(model.3)
```  

GRIP * .02447 + ARM * .037 = SIMS 
the bigger the adjusted R square the bigger the model, the multiple R squared is always a little bit bigger than the adjusted R square. the bigger the adjusted R square the bigger we reduce the errors.  

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

the model must be nested. that means that all the independent variables in one model are also in the other models SIMS is a function of ARM. model.2 is nested in model.3, model.1 is nested in model.3 

## Informally compare Model.1 with model.2

